---
title: "Course Project Complimentary doc"
author: "Miguel Rayon"
date: "Wednesday, February 24, 2016"
output: html_document
---

This document serves as a complimentary explanation to the Course project document

First, unload the datasets (included also in this repository)
Then check the web from <http://groupware.les.inf.puc-rio.br/har>. 

All this data is avalaible thanks to the authors of th paper:
Velloso, E.; Bulling, A.; Gellersen, H.; Ugulino, W.; Fuks, H.[Qualitative Activity Recognition of Weight Lifting Exercises](http://groupware.les.inf.puc-rio.br/work.jsf?p1=11201). Proceedings of 4th International Conference in Cooperation with SIGCHI (Augmented Human '13) . Stuttgart, Germany: ACM SIGCHI, 2013.

Read more: <http://groupware.les.inf.puc-rio.br/har#ixzz416gWFNxX>
First let's load the data an perform some checks

```{r echo=FALSE}
setwd("D:/Datos Miguel Rayon/Casa/Documents/Curso Data Science J Hopkins/Machine Learning/project/Coursera_ML_Project")
```


```{r}
trainset<-read.csv("pml-training.csv",header=T)
head(trainset)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
